\documentclass[12pt]{article}
\usepackage{hyperref}
\title{Open \LaTeX{} Studio 1.0}
\date{}
\author{Sebastian Brudzinski}
\begin{document}
  \maketitle
  \section{Welcome}
  Thanks for trying out the Open \LaTeX{} Studio - an Open Source \LaTeX{} editor. Please note, that the
  application is in constant development. You might encounter some bugs or inconveniences. If that happens, 
  we would be extremely thankful, for letting us know about encountered problems. Any ideas or new feature
  requests are welcome as well! Please see the project page at 
  \url{https://github.com/sebbrudzinski/Open-LaTeX-Studio}
  or contact author via
  \href{mailto:seb.brudzinski@gmail.com}{seb.brudzinski@gmail.com}

  \section{Features}
  New features and fixes are added to the project on a regular basis. Currently, the application provides
  a nifty code editor, with syntax highlight and basic code completion. The preview of the document is automatically
  generated in the PDF Preview window. You can also save your tex documents or generate PDF documents from your
  \LaTeX{} code. For the application to work, it is necessary to have the path to the pdflatex set in an 
  environment variable (or in non-technical speech - it must be possible to invoke pdflatex from any place
  in your command line terminal). If you cannot see anything in the PDF preview window, it most likely means that
  the path is not set.

  \section{Contribute}
  Are you a developer and would like to contribute to the project? Take a look at the link provided in section one, 
  and simply find something to work on. The issue tracker is constantly updated with user feedback. You can also
  find some useful information on the project wiki.
\end{document}
